\vspace*{1.5mm}
\block{\strut Introduction}{
        
        \vspace{0.5cm}

        Electron microscopy allows us to study the structure of objects much smaller than the wavelength of visible light.
        In the field of nanoparticles, \textbf{high-resolution transmission electron microscopy (HRTEM)} enables us to investigate the \textbf{structure and geometry of nanoalloys}.
        However, analyzing HRTEM images can be time-consuming and challenging.
        It needs a lot of expertise and experience in the imaging field to analyze them correctly.
        The use of deep learning can be an option to accelerate and simplify the analysis of these HRTEM images and exctract information about the structure and properties of nanoalloys.
        For the training of the \textbf{deep learning} models, a comprehensive dataset is needed.
        We generate this dataset using a snapshots extracted from \textbf{molecular dynamics} simulations coupled to the generation of synthetic HRTEM images using the multi-slice technique.
        
        \vspace{2cm}
        
        We focus here on the \textcolor{colorAg}{\textbf{Ag}}–\textcolor{colorCo}{\textbf{Co}} system, an immiscible alloy with a known structure.
        In this system, \textcolor{colorAg}{\textbf{Ag}} atoms preferentially segregate to the surface while \textcolor{colorCo}{\textbf{Co}} atoms tend to form the core. This is expected as \textcolor{colorAg}{\textbf{Ag}} has a lower surface energy when compared to \textcolor{colorCo}{\textbf{Co}} and additionally \textcolor{colorAg}{\textbf{Ag}} atoms are larger.
        Yet, depending on the synthesis conditions, the structure of these nanoalloys varies and can be found in metastable conformations, ranging from core-shell to Janus or even partially mixed structures.
        The use of deep learning models can help us to extract information about their structure and properties.

        %        The objective with this system is to check if the deep learning models can learn and extract the same information from the HRTEM images.
%        Once this objective is done, other systems with more complex structures that we don't know yet will be studied to extract new information about their structure and properties.

        \vspace{3cm}

}